### 2019-10-07 abstract.tex
Final version

%\begin{resumen}

%\end{resumen}

@@

This Master thesis recapitulates the last years of the TraMoS project, on which new targets were selected, modern tools were used and new analysis was performed. I studied 27 new light curves of three hot Jupiters: WASP-18b, WASP-19b, and WASP-77Ab. Their orbital and physical parameters were refined, and their linear ephemeris updated thanks to the inclusion of archival transit time data. Given the lack of significant variations in their transit times, dynamical analysis can place upper mass limits in hypothetical perturbers. Bodies with masses greater than $50\,M_{\odot}$ can be discarded for WASP-18b, $6\,M_{\odot}$ for WASP-19b, and $10\,M_{\odot}$ for WASP-77Ab. Furthermore, I included recent TESS data for the three targets, supporting the linear ephemeris as the best fit for their transit times

The results presented in this thesis support the rare occurrence of companions in hot Jupiters systems. Further studies may confirm if this kind of planet goes through a different formation process ending up orbiting alone on their systems or they have very small and unseen companions.

>>>>

\begin{resumen}
El proyecto Transit Monitoring in the South (TraMoS) busca realizar seguimiento fotométrico de exoplanetas transitantes conocidos. Este proceso provee no sólo información acerca del planeta transitante, sino también sobre la arquitectura del sustema planetario. Desviaciones de la efemeris lineal producida por el movimiento Kepleriano, conocidas como Transit Timing Variations (TTV), sólo se pueden detectar mediante intensivo seguimiento y pueden sugerir la existencia de cuerpos adicionales en el sistema, tales como compañeros planetarios o exolunas.

Esta tesis de magíster recapitula los últimos años del proyecto TraMoS, se seleccionaron nuevos objetivos, se utilizaron nuevas heramientas, y se desarrollaron nuevos analisis. Se estudiaron 27 nuevas curvas de luz de tres Jupiter calientes: WASP-18b, WASP-19b, y WASP-77Ab. Se refinaron sus parámetros físicos y orbitales, y la ecuación de efemeris lineal fue actualizada gracias a la inclusión de datos de transito históricos. Debido a la carencia de variaciones significativas en sus tiempos central de tránsito, la realización de análisis dinámicos puede imponer límites superiores a la masa de perturbadores hipotéticos. Se descartaron cuerpos que poseen masas más grandes que $50\,M_{\oplus}$ para WASP-18b, $6\,M_{\oplus}$ para WASP-19b, y $10\,M_{\oplus}$ para WASP-77Ab. Adicionalmente, se incluyeron datos de TESS para los tres objetivos, lo que apoya que la efemeris lineal es el mejor modelo para los tiempos de tránsito.

Los resultados presentados en esta tesis apoyan la poco frecuente aparición de compañeros en sistemas de Júpiters calientes. Estudios futuros podrían evidenciar si estos tipos de planeta sufrieron un proceso de formación diferente por el cual terminan orbitando solos, o si efectivamente poseen compañeros enanos que no se han detectado.
\end{resumen}

@@

This Master thesis recapitulates the last years of the TraMoS project, on which new targets were selected, modern tools were used and new analysis was performed. I studied 27 new light curves of three hot Jupiters: WASP-18b, WASP-19b, and WASP-77Ab. Their orbital and physical parameters were refined, and their linear ephemeris updated thanks to the inclusion of archival transit time data. Given the lack of significant variations in their mid-transit times, dynamical analysis can place upper mass limits in hypothetical perturbers. Bodies with masses greater than $50\,M_{\oplus}$ can be discarded for WASP-18b, $6\,M_{\oplus}$ for WASP-19b, and $10\,M_{\oplus}$ for WASP-77Ab. Furthermore, I included recent TESS data for the three targets, supporting the linear ephemeris as the best fit for their transit times.

The results presented in this thesis support the rare occurrence of companions in hot Jupiter systems. Further studies may confirm if this kind of planet goes through a different formation process ending up orbiting alone on their systems or they have very small and unseen companions.

### 2019-10-07 conclusion.tex
Final version

The TraMos project started more than 10 years ago aiming to refine orbital and physical parameters of already known exoplanets, and to search for variation in the transit time -- or other planet parameters -- that could suggest the existence of smaller bodies on their systems. Since the beginning, the targets have been hot Jupiters due to their short-periods, allowing to obtain more consecutive transit light curves in a reduced period.

@@

During this Master project, I studied three exoplanets: WASP-18b, WASP-19b, and WASP-77Ab. For these targets, I analyzed a total of twenty-six new light curves: eight of WASP-18b, nine of WASP-19b and nine of WASP-77Ab. In the case of WASP-77Ab, four light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{var2.astro.cz/ETD}} to obtain a wider time coverage. For the light curves coming from the TraMoS project, I started from performing aperture photometry of the targets using our data reduction pipeline (for further details see \ref{chap:pipeline}), to obtain high-precision light curves. Then, I used EXOFASTv2 \cite{Eastman2013,Eastman2017} to get the best fit for the light curve's data and hence, to refine their orbital and physical parameters and obtain their transit times.

The TTV curves were constructed from the residuals between the observed transit time and the expected from the linear ephemeris. None of the targets studied in this thesis shows a clear, periodic sinusoidal signal in the variation of their transit times and moreover, the structure of the transit times are comparable with a random distribution after a Lomb-Scargle analysis. This suggests the lack of close-in companions in MMR in their systems. However, upper mass limits of hypothetical perturbers -- placed not only in near MMR -- could be computed with the time-scatter from the linear ephemeris. The hot Jupiter WASP-18b shows 83 seconds of scatter, WASP-19b shows 75 seconds and WASP-77ab shows 121 seconds. The latter being the target with a larger deviation from the linear ephemeris, but at the same time, the target with fewer transit times.

In summary, the upper mass limit for possible perturbers that could produced the observed scatter in the transit time are:
\begin{itemize}
\item WASP-18b: $1.9\,M_{\odot}$, $4.0\,M_{\odot}$, $5.0\,M_{\odot}$, $25\,M_{\odot}$, $10\,M_{\odot}$, $7.0\,M_{\odot}$, $50\,M_{\odot}$ in 1:3, 2:5, 1:2, 2:1, 5:2, 3:1 and 4:1 resonances, respectively. 
\item WASP-19b: $2.0\,M_{\odot}$, $6.0\,M_{\odot}$, $0.9\,M_{\odot}$, $3.0\,M_{\odot}$, $2.0\,M_{\odot}$ in 1:2, 5:3, 2:1, 5:2 and 3:1 resonances, respectively. 
\item WASP-77Ab: $1.0\,M_{\odot}$, $3.5\,M_{\odot}$, $2.0\,M_{\odot}$, $7.0\,M_{\odot}$, $6.0\,M_{\odot}$, $10\,M_{\odot}$, $3.5\,M_{\odot}$, $4.5\,M_{\odot}$ in 1:3, 1:2, 3:5, 2:3, 5:3, 7:4, 2:1 and 3:1 resonances, respectively.
\end{itemize}

@@

To date, none of the previous and current targets of the TraMoS project have shown TTVs. As they are all hot Jupiters, these studies support the theory of "alone hot Jupiters", on which this kind of exoplanets are probably alone in their systems or accompanied of small bodies, not in MMR. How WASP-47b and Kepler-730b, the only two hot Jupiters showing TTVs, have close-in companions is still unknown. The migration theory of hot Jupiters could give us a possible explanation of how these gas giant ended-up with companions in MMR, as they are supposed to start their migration process in far-away orbits. While migrating, they could catch other bodies to then settling down in close orbits. But the lack of more hot Jupiters with TTVs suggest that probably during migration they cleaned-up their orbits of small bodies.

The TraMoS catalog stores more than 400 transits events of near 140 exoplanets. As future work, I propose to continue performing a ground-based photometric follow-up of the targets in this catalog, as well as new targets, combining the efforts with TESS data of Sector 1 to 13. In this way, we could obtain better estimations of TTVs with wider time-span data from TraMoS, and an important amount of consecutive transit times from TESS. In the near future, given the new scatter of the transit time in the three targets analyzed in this thesis, more accurate upper mass limits for hypothetical perturbers could be computed. Also, I will analyze the exoplanets WASP-36b and HATS-34b, which each one has five transit times from TraMoS and twelve and twenty-six from TESS, respectively. For WASP-22, WASP-46, WASP-45, WASP-23, and WASP-123, TESS provided five, seventeen, eight, seven and thirteen light curves, respectively. These targets are within the 30 targets with most light curves from TraMoS, therefore, they should be the next in line.

The reduction pipeline is fully functional and provides high-precision photometry, nevertheless, several improvements were left behind because of the lack of time to implement them. For example, the coordinates selection could be done inside the program, to avoid mistakes when typing them by hand before calling the pipeline. Any new idea to improve the reduction pipeline could be done within an undergrad project or graduate semester-workshop.

>>>>

The TraMos project started more than 10 years ago aiming to refine orbital and physical parameters of already known exoplanets, and to search for variation in the transit time -- or other planet parameters -- that could suggest the existence of additional massive bodies on their systems. Our search focused on hot Jupiter planetary systems on short orbital periods, allowing to obtain additional photometric data from ground as well as space-based telescopes.

@@

During this Master project, I studied three exoplanets: WASP-18b, WASP-19b, and WASP-77Ab. For these targets, I analyzed a total of twenty-six new light curves: eight of WASP-18b, nine of WASP-19b and nine of WASP-77Ab. In the case of WASP-77Ab, four light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{https://var2.astro.cz/ETD}} to obtain a wider time coverage. For the light curves coming from the TraMoS project, I started from performing aperture photometry of the targets using our data reduction pipeline (for further details see Appendix \ref{chap:pipeline}), to obtain high-precision light curves. Then, I used EXOFASTv2 \cite{Eastman2013,Eastman2017} to get the best fit for the light curve's data and hence, to refine their orbital and physical parameters and obtain their transit times.

The TTV curves were constructed from the residuals between the observed transit time and the expected from the linear ephemeris. None of the targets studied in this thesis shows a clear, periodic sinusoidal signal in the variation of their transit mid-times and moreover, the structure of the transit times are comparable with a random distribution after a Lomb-Scargle analysis. This suggests the lack of close-in companions in MMR in their systems. However, upper mass limits of hypothetical perturbers -- placed not only in near MMR -- could be computed with the time-scatter from the linear ephemeris. The hot Jupiter WASP-18b shows 83 seconds of scatter, WASP-19b shows 75 seconds and WASP-77ab shows 121 seconds. The latter being the target with a larger deviation from the linear ephemeris, but at the same time, the target with fewer transit times.

In summary, the upper mass limit for possible perturbers that could produced the observed scatter in the transit time are:
\begin{itemize}
\item WASP-18b: $1.9\,M_{\oplus}$, $4.0\,M_{\oplus}$, $5.0\,M_{\oplus}$, $25\,M_{\oplus}$, $10\,M_{\oplus}$, $7.0\,M_{\oplus}$, $50\,M_{\oplus}$ in 1:3, 2:5, 1:2, 2:1, 5:2, 3:1 and 4:1 resonances, respectively. 
\item WASP-19b: $2.0\,M_{\oplus}$, $6.0\,M_{\oplus}$, $0.9\,M_{\oplus}$, $3.0\,M_{\oplus}$, $2.0\,M_{\oplus}$ in 1:2, 5:3, 2:1, 5:2 and 3:1 resonances, respectively. 
\item WASP-77Ab: $1.0\,M_{\oplus}$, $3.5\,M_{\oplus}$, $2.0\,M_{\oplus}$, $7.0\,M_{\oplus}$, $6.0\,M_{\oplus}$, $10\,M_{\oplus}$, $3.5\,M_{\oplus}$, $4.5\,M_{\oplus}$ in 1:3, 1:2, 3:5, 2:3, 5:3, 7:4, 2:1 and 3:1 resonances, respectively.
\end{itemize}

@@

To date, none of the previous and current targets of the TraMoS project have shown TTVs. As they are all hot Jupiters, these studies support the theory of "isolated hot Jupiters", on which this kind of exoplanets are probably alone in their systems or accompanied of small bodies, not in MMR. How WASP-47b and Kepler-730b, the only two hot Jupiters showing TTVs, have close-in companions is still unknown. The migration theory of hot Jupiters could give us a possible explanation of how these gas giant ended-up with companions in MMR, as they are supposed to start their migration process in far-away orbits. While migrating, they could catch other bodies to then settling down in close orbits. But the lack of more hot Jupiters with TTVs suggest that probably during migration they cleaned-up their orbits of small bodies.

The TraMoS catalog stores more than 400 transits events of near 140 exoplanets. As future work, I propose to continue performing a ground-based photometric follow-up of the targets in this catalog, as well as new targets.  Combining the efforts of TESS and TraMoS the amount of mid-transit times will cover a wider time-span and hence detect possible long-periodic TTV trends. TESS can provide hints of possible short and long-term TTVs -- or TPVs in general -- with an important amount of consecutive transit light curves. Then, performing ground-based follow-up is the most efficient way to prove or discard this variations, as the number of possible transit data from TESS is constrain by the duration of the sectors -- for most of the targets --. We proved that our current used telescopes provides high-precision light curves, comparable with TESS.

% with TESS data of Sector 1 to 13. In this way, we could obtain better estimations of TTVs with wider time-span data from TraMoS, and an important amount of consecutive transit times from TESS.

In the near future, given the new scatter of the transit time in the three targets analyzed in this thesis, more accurate upper mass limits for hypothetical perturbers could be computed. Also, the next step is to analyze the exoplanets WASP-36b and HATS-34b, which each one has five transit times from TraMoS and twelve and twenty-six from TESS, respectively. For WASP-22, WASP-46, WASP-45, WASP-23, and WASP-123, TESS provided five, seventeen, eight, seven and thirteen light curves, respectively. These targets are within the 30 targets with most light curves from TraMoS, therefore, they should be the next in line.

The reduction pipeline is fully functional and provides high-precision photometry. During this thesis project, I included dictionaries that allows the reduction photometry of new telescopes. Currently, the pipelines works for data coming from: Danish 1.54 m, Warsaw, Swope, Du Pont, REM, SMARTS 0.9 m and 1 m and SOAR. Nevertheless, several improvements were left behind because of the lack of time to implement them. For example, the coordinates selection could be done inside the program, to avoid mistakes when typing them by hand before calling the pipeline. Any new idea to improve the reduction pipeline could be done within an undergrad project or graduate semester-workshop.

### 2019-10-07 introduction.tex
Final version

\chapter{Introduction}\label{chap:intro}
The idea of the existence of planets orbiting other stars different from our Sun lived in the human imagination for centuries. During the sixteenth century, the Italian philosopher Giordano Bruno suggested, for the first time in history, that more planets could be outside the Solar System. Even though the first claims of exoplanet detection began at the begin of the twentieth century\footnote{The van Maanen 2 star, which later was confirmed as a white dwarf.}, it was not until more than four hundred years after Bruno's statement, that the first exoplanet was confirmed in 1992. Surprisingly, it was not just one exoplanet but three, orbiting the pulsar PSR B1257+12 more than 1000 light-years away from us. Today, more than 4,000 exoplanets are confirmed, and thousands more are waiting for their confirmation.

Having billions of billions of galaxies in the Universe each one with millions of stars, the current number of discovered exoplanets is still very low. Furthermore, the distance at which we can detect exoplanets is limited by our current technology, thus finding a candidate in the closer galaxy -- Andromeda -- could be considered science fiction. If the Milky Way has \textit{only} around $2\,\times10^{11}$ stars, how could be the Solar System unique? How could be the Earth the only planet with life on it? Until today, it is still difficult to answer those questions. The Solar System presents a logic structure where the small, rocky planets are closer to the Sun, and the gas giants are located beyond. But no other exoplanetary system have been found having similar features and even not exoplanetary life has been detected yet\footnote{By the date of writing this thesis.}. Our knowledge about the Solar System challenges the existence of other kinds of planetary architectures with close-in gas giants, for instance, suggesting that there is not a single, universal planetary process formation. Answering such questions makes studying exoplanets a relevant matter nowadays.

The discovery of three exoplanets orbiting the pulsar PSR B1257+12 is still very rare. The technique used to find them is called Pulsar Timing and it consists in measuring the variation of a pulsar's pulsation period due to the presence of a body orbiting it. As pulsars are not very common and we know that planet may be orbiting main-sequence stars -- as the Earth and all the Solar System --, the latter become the principal target on which the hunting of exoplanet is dedicated. Planets are small when compare to their host star, that is why most of the current discovery techniques are focused on observing the effects in the stars, or how what we observed from them changed, caused by the presence of planets. Nevertheless, Direct Imaging is the only technique in which the planet is observed directly but the star needs to be covered to only received the thermal emission produced by the planet.

Microlensing is different from all the other discovery techniques because a third, bright background star is required to obtain the desired effect: gravitational lensing produced by the star with a planet (multiple lenses). As the primary lens is small -- around $1\,M_{\odot}$ -- the two images produced by the gravitational lensing are very close between each other and the event can not be resolved. The presence of a planet will cause a deviation in the magnification curve of the event. On the other hand, Astrometry measurements can be used to discover exoplanets too. With the current high-precision in the position of the stars, even their displacement in the sky can be detected. Similar to the Radial Velocity technique, through Astrometry the displacement of the star due to the gravity of a planet is measured.

The two techniques that have contributed the most to the discovery of extrasolar planets are Radial Velocity and Transits (see Figure \ref{exoplanets}). Each one of these techniques had their own advantages depending on the physical properties of the planetary system. When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases, proportionally to the radius of the planet. Thus, the radius ratio between the planet and the star, $R_{p}/R_{*}$ can be determined directly using the Transit method. On the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center. Therefore, the star will move in its own small orbit with a radius proportional to the mass of the planet. In this case, the Radial Velocity method unveils the planet's minimum mass $M_{p}\sin i$.

Anyway, the rising research field of exoplanets does not end with their discovery. Performing follow-up and proper characterization of discovered exoplanets are essential to obtain a full list of orbital and planetary parameters. For instance,  39\%  of the total number of discovered exoplanets have a proper measurement of their masses, and only 17\% have their mass and radius computed\footnote{Information obtained from the NASA Exoplanet Archive Database \url{exoplanetarchive.ipac.caltech.edu}}.

@@

The perfect scenario comes when both methods, Transits and Radial Velocity, can be used in the same planetary system, allowing to derive essential properties of the planet. Combining Transits and Radial Velocity follow-up the whole system can be characterized. From Transits we get the orbital inclination, then the real mass can be computed with Radial Velocity measurements. From Transits we get the radius ratio of the system, assuming that the star is previously well characterized, the radius of the planet is derived. Then, as we already have the mass of the planet, the mean density can be estimated. This parameter gives a clue about the possible composition of the planet. Moreover, if the follow-up is performed combining Transits with big telescopes, for instance, the Very Large Telescope, important information about the planet can be unveiled, even their atmospheric composition and dynamics.

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{imagenes/exoplanets_hd.pdf}
\caption{Mass and orbital period distribution of Exoplanets, and their corresponding discovery methods in color. This plot only shows the exoplanets with measured masses. The Transit and Radial Velocity methods (in orange and blue, respectively) are the most successful techniques to discover extrasolar planets. However, both techniques are still more sensitive to detect Jupiter-mass planets rather than Earth-mass, but the Transit method is more sensitive to short-period planets.}
\label{exoplanets}
\end{figure}

@@

Continued photometric monitoring not only increased the precision of planetary parameters but provides potential information about the planet and its environment. Through the observation of transit events during several epochs, variability in the planetary system can be detected. For instance, the first measurement of two planets gravitationally bounded was made by \citep{Holman2010}, this discovery was made thanks to the continued observations performed by the Kepler mission. This phenomenon is detectable observing during several epochs just one of the planets involved and analyzing how the presence of a companion produces such variability. Moreover, variability in transiting exoplanets -- specifically in the time of the transit -- can be attributed not only to planetary companions, but exomoons\citep{Kipping2009a,Kipping2009b}, tidal orbital decay\citep{Hoyer2016,Hoyer2016b}, secular orbits changes\citep{Adams2006} or relativistic effects \citep{Heyl2007}, among others.

The Transit Monitoring in the South project (TraMoS) is one of its kind in the southern hemisphere, aiming to detect multi-exoplanetary systems trough the variability in transit parameters of transiting exoplanets. To achieve this goal, extensive photometric follow-up of transiting exoplanets is being carry-on, using one-meter class telescopes located in Chile.

@@

This thesis is organized as follows: Chapter \ref{chap:tramos} summarizes the TraMoS project, its goals, techniques, and achievements to date. Also, this chapter includes what we can learn from transit exoplanets' light curves and Transit Timing Variations. Chapter \ref{chap:paper} shows the analysis and results of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab, including their observations and data reduction, light curve and RV analysis, measurements of TTVs and an upper mass limit for possible companions in their systems. Then, Chapter \ref{chap:tess}  recapitulates the current stage of the TraMoS project on which TESS data is being incorporated. Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS. Finally, Chapter \ref{chap:conclusion} contains a summary of this thesis as well as some ideas for future work. The Appendix section includes a brief description of the aperture photometry pipeline utilized, all the Python scripts used to generate each light curve, and an example of the PDF file obtained after the aperture photometry procedure.

>>>>

\chapter{Introduction}\label{chap:intro}
The idea of the existence of planets orbiting other stars different from our Sun has lived in the human imagination for centuries. During the sixteenth century, the Italian philosopher Giordano Bruno suggested\footnote{In the book: \textit{De l'infinito, universo e mondi}, 1584}, for the first time in history, that more planets could be outside the Solar System. More than four hundred years after Bruno's statement, the first exoplanet was confirmed in 1992. Surprisingly, it was not just one exoplanet but three, orbiting the pulsar PSR B1257+12 more than 1000 light-years away from us. Today, more than 4,000 exoplanets are confirmed, and thousands more are waiting for their confirmation.

%Even though the first claims of exoplanet detection began at the begin of the twentieth century\footnote{The van Maanen 2 star, which later was confirmed as a white dwarf.}, it was not until more than four hundred years after Bruno's statement, that

Having billions of billions of galaxies in the Universe each one with millions of stars, the current number of discovered exoplanets is still very low. Furthermore, the distance at which we can detect exoplanets is limited by our current technology, thus finding a candidate in the closer galaxy -- Andromeda -- could be considered science fiction. If the Milky Way has \textit{only} around $2\,\times10^{11}$ stars, how could be the Solar System unique? How could the Earth be the only planet with life on it? Until today, it is still difficult to answer those questions. The Solar System presents a logic structure where the small, rocky planets are closer to the Sun, and the gas giants are located beyond. But no other exoplanetary system has been found having similar features and even not exoplanetary life has been detected yet. Our knowledge about the Solar System challenges the existence of other kinds of planetary architectures with close-in gas giants, for instance, suggesting that there is not a single, universal planetary process formation. Answering such questions makes studying exoplanets a relevant matter nowadays.

The discovery of three exoplanets orbiting the pulsar PSR B1257+12 is still very rare. The technique used to find them is called Pulsar Timing and it consists in measuring the variation of a pulsar's pulsation period due to the presence of a body orbiting it. As pulsars are not very common and we know that planet may be orbiting main-sequence stars -- as the Earth and all the Solar System --, they become the principal target on which the hunting of exoplanet is dedicated. Planets are small when compare to their host star, that is why most of the current discovery techniques are focused on observing the effects in the stars, or how what we observed from them changed, caused by the presence of planets.

The most used and successful planet detection techniques are: transits, radial velocity, direct imaging, microlensing and astrometry. Direct imaging is the only technique in which the planet is observed directly but the star needs to be masked in order to only received the thermal emission from the planet. Microlensing is different from all the other discovery techniques because a background star is required to obtain the desired effect: gravitational lensing produced by the star with a planet (multiple lenses). As the primary lens is small -- around $1\,M_{\odot}$ -- the two images produced by the gravitational lensing effect are very close to each other and cannot be resolved with current imaging techniques. The presence of a planet in orbit around the lens star will cause a deviation in the magnification curve of the event. On the other hand, astrometry measurements can be used to discover exoplanets too. With the current high-precision in the position of the stars, even their displacement in the sky can be detected. Similar to the radial velocity technique, through astrometry the displacement of the star due to the gravity of a planet is measured.

The two techniques that have contributed the most to the discovery of extrasolar planets are radial velocity and transits (see Figure \ref{exoplanets}). Each one of these techniques had their own advantages depending on the physical properties of the planetary system. When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases, proportionally to the square of the ratio between the radius of the planet and the star. Thus, the radius ratio between the planet and the star, $R_{p}/R_{*}$ can be determined directly using the transit method. On the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center. Therefore, the star will move in its own small orbit with a radius proportional to the mass of the planet. In this case, the radial velocity method unveils the planet's minimum mass $M_{p}\sin i$.

Anyway, the rising research field of exoplanets does not end with their discovery. Performing follow-up and proper characterization of discovered exoplanets are essential to obtain a full list of orbital and planetary parameters. For instance,  39\%  of the total number of discovered exoplanets have a proper measurement of their masses, and only 17\% have their mass and radius computed\footnote{Information obtained from the NASA Exoplanet Archive Database \url{https://exoplanetarchive.ipac.caltech.edu}}.

@@

One of the perfect scenarios comes when the two methods, transits and radial velocity, can be used in the same planetary system, allowing to derive essential properties of the planet and its orbit. Combining transits and radial velocity follow-up the whole system can be characterized. From transits we get the orbital inclination, then the real mass can be computed with radial velocity measurements. From transits we get the radius ratio of the system, assuming that the star is previously well characterized, the radius of the planet is derived. Then, as we already have the mass of the planet, the mean density can be estimated. This parameter gives a clue about the possible composition of the planet. Moreover, if the follow-up is performed combining transits with big telescopes, important information about the planet can be unveiled, perhaps even their atmospheric composition and dynamics.

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{imagenes/exoplanets_hd.pdf}
\caption{Mass and orbital period distribution of Exoplanets, and their corresponding discovery methods in color. This plot only shows the exoplanets with measured masses. The transit and radial velocity methods (in orange and blue, respectively) are the most successful techniques to discover extrasolar planets. However, both techniques are still more sensitive to detect Jupiter-mass planets rather than Earth-mass, but the Transit method is more sensitive to short-period planets.}
\label{exoplanets}
\end{figure}

@@

Continued photometric monitoring not only increased the precision of planetary parameters but provides potential information about the planet and its environment. Through the observation of transit events during a long observing baseline, variability in the planetary system can be detected. For instance, the first measurement of two planets gravitationally bounded was made by \citep{Holman2010}, this discovery was made thanks to the continued observations performed by the Kepler mission. This phenomenon is detectable by observing the same transit event multiple times over an extended number of epochs. Any variability in the mid-transit times could be attributed to an additional body. Moreover, variability in transiting exoplanets -- specifically in the time of the mid-transit -- can be attributed not only to planetary companions, but exomoons\citep{Kipping2009a,Kipping2009b}, tidal orbital decay\citep{Hoyer2016,Hoyer2016b}, secular orbits changes\citep{Adams2006} or relativistic effects \citep{Heyl2007}, among others.

The Transit Monitoring in the South project (TraMoS) aims to detect multi-exoplanetary systems trough the variability in parameters of transiting exoplanets. To achieve this goal, extensive photometric follow-up of transit is being carried on, using one-meter class telescopes located in Chile.

@@

This thesis is organized as follows: Chapter \ref{chap:tramos} summarizes the TraMoS project, its scientific goals, techniques, and achievements to date. Also, this chapter describes what we can learn from transit exoplanets' light curves and Transit Timing Variations. Chapter \ref{chap:paper} shows the analysis and results of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab, including their observations and data reduction, light curve and RV analysis, measurements of TTVs and an upper mass limit for possible companions in their systems. Then, Chapter \ref{chap:tess}  recapitulates the current stage of the TraMoS project on which TESS data is being incorporated. Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS. Finally, Chapter \ref{chap:conclusion} contains a summary of this thesis as well as some ideas for future work. The Appendix section includes a brief description of the aperture photometry pipeline utilized, all the Python scripts used to generate each light curve, and an example of the PDF file obtained as a result of the aperture photometry procedure.

### 2019-10-07 paper.tex
Final version

We present 22 new transit observations for the exoplanets WASP-18b, WASP-19b, and WASP-77Ab, from the Transit Monitoring in the South (\emph{TraMoS}) project. We simultaneously model our newly collected transit light curves, as well as archival photometry and radial velocity data to obtain refined physical and orbital parameters. We did not find significant $\rm TTV_{RMS}$ variations larger than 83, 75, and 121 seconds for WASP-18b, WASP-19b, and WASP-77Ab, respectively. Dynamical simulations were carried out to constrain the masses of a possible perturber. The observed RMS could be produced by a perturber body with an upper limit mass of 5 and $7~M_{\oplus}$ in 1:2 and 3:1 resonance, and $25~M_{\oplus}$ in 2:1 resonance for WASP-18b. In the case of WASP-19b, companions with masses up to 0.9, 2 and $6~M_{\oplus}$, in 2:1, 3:1, and 5:3 resonances, reproduce the RMS. In this system, we also discard a hypothetical perturber of $500~M_{\oplus}$ in 1:3 resonance, because of the mass limit from RV variations. For WASP-77Ab a planet with masses between $1-7~M_{\oplus}$ in 1:2, 1:3, 2:1, 2:3, 3:1, 3:5, 5:3 resonances could reproduce the observed RMS in the TTVs. Finally, using a Lomb-Scargle period search we find no evidence of a periodic trend on our TTV data for the three exoplanets.

>>>>

We present 22 new transit observations for the exoplanets WASP-18b, WASP-19b, and WASP-77Ab, from the Transit Monitoring in the South (\emph{TraMoS}) project. We simultaneously model our newly collected transit light curves, as well as archival photometry and radial velocity data to obtain refined physical and orbital parameters. We did not find significant $\rm TTV_{RMS}$\footnote{RMS: root-mean-square} variations larger than 83, 75, and 121 seconds for WASP-18b, WASP-19b, and WASP-77Ab, respectively. Dynamical simulations were carried out to constrain the masses of a possible perturber. The observed RMS could be produced by a perturber body with an upper limit mass of 5 and $7~M_{\oplus}$ in 1:2 and 3:1 resonance, and $25~M_{\oplus}$ in 2:1 resonance for WASP-18b. In the case of WASP-19b, companions with masses up to 0.9, 2 and $6~M_{\oplus}$, in 2:1, 3:1, and 5:3 resonances, reproduce the RMS. In this system, we also discard a hypothetical perturber of $500~M_{\oplus}$ in 1:3 resonance, because of the mass limit from RV variations. For WASP-77Ab a planet with masses between $1-7~M_{\oplus}$ in 1:2, 1:3, 2:1, 2:3, 3:1, 3:5, 5:3 resonances could reproduce the observed RMS in the TTVs. Finally, using a Lomb-Scargle period search we find no evidence of a periodic trend on our TTV data for the three exoplanets.

### 2019-10-07 pipeline.tex
Final version

Since the beginning of the TraMoS project, an aperture photometry pipeline has been in development, on which several graduates and undergraduates students worked and are currently working on it. This pipeline is Python-based and includes standard procedures of reduction, calibrations, and aperture photometry, including bias and flat-field corrections. The user needs to give the coordinates of the target and reference stars and a range of pixels for a possible aperture. Then, to produce high-precision light curves of the target and reference stars, the pipeline semi-automatic finds the best aperture and ring size, for the sky that produces the less RMS in the light curves.

The pipeline works with a specific directories' structure where all the needed information should be:
\begin{itemize}
\item raw: Folder containing the raw data of the observations. It could be fits files or compressed fits (e.g \textit{fit.ZIP}).
\item calib: This folder should include the flats -- sky or dome -- and bias files.
\item data: Empty folder which will contain the output data after the aperture photometry procedure.
\item figures: Empty folder on which all the figures generated in the reduction process will be stored.
\item log: Folder containing the Python script to run the pipeline for the specific data set.
\item extraction.tex: Latex file which generates the PDF file with all the important information related to the aperture photometry procedure process, such as images of the stamps, the radial profile of the target star, FWHM plots, preview of the light curve, etc.
\item tramos\_custom.sty: A customizable file containing the information related to the telescope, target's name, filter, date of the observation, RA, DEC and target's magnitude. When the pipeline finishes, it fills this file with the best aperture size obtained.
\end{itemize}

I have implemented dictionaries to ease the use of the pipeline with different telescopes. One of the biggest problems that I faced when I started reducing data, was the distinctness between the headers produced from different telescopes. For example, while some of them recorded the type of filter as \textit{FILTER}, others use \textit{FILTERB}. Also, as the TraMoS project has been collecting data for more than 10 years ago, some of our used telescopes were updated with new CCDs, producing that the pipeline was no longer functional. Currently, the pipeline works with data from the following telescopes: 
\begin{itemize}
\item La Silla Observatory: Danish 1.54 m (previous and after 2017) and REM.
\item Cerro Tololo Inter-American Observatory: SMARTS 0.9 m and 1 m.
\item Las Campanas Observatory: Warsaw, Swope, Du Pont.
\item Cerro Pachón: SOAR
\end{itemize}

>>>>

Since the beginning of the TraMoS project, an aperture photometry pipeline has been in development, on which several graduates and undergraduates students worked and are currently working on it. This pipeline is Python-based and includes standard procedures of reduction, calibrations, and aperture photometry, including bias and flat-field corrections. The user needs to give the coordinates of the target and reference stars and a range of pixels for a possible aperture. Then, to produce high-precision light curves of the target and reference stars, the pipeline semi-automatically finds the best aperture and ring size, for the sky that produces the less RMS in the light curves.

The pipeline works with a specific directories' structure where all the needed information should be:
\begin{itemize}
\item raw: Folder containing the raw data of the observations. It could be FITS files or compressed FITS (e.g \textit{fit.ZIP}).
\item calib: This folder should include the flats -- sky or dome -- and bias files.
\item data: Empty folder which will contain the output data after the aperture photometry procedure.
\item figures: Empty folder on which all the figures generated in the reduction process will be stored.
\item log: Folder containing the Python script to run the pipeline for the specific data set.
\item extraction.tex: Latex file which generates the PDF file with all the important information related to the aperture photometry procedure process, such as images of the stamps, the radial profile of the target star, FWHM plots, preview of the light curve, etc.
\item tramos\_custom.sty: A customizable file containing the information related to the telescope, target's name, filter, date of the observation, RA, DEC and target's magnitude. When the pipeline finishes, it fills this file with the best aperture size obtained.
\end{itemize}

I have implemented dictionaries to ease the use of the pipeline with different telescopes. One of the biggest problems that I faced when I started reducing data, was the distinctness between the FITS headers produced from different telescopes. For example, while some of them recorded the type of filter as \textit{FILTER}, others use \textit{FILTERB}. Also, as the TraMoS project has been collecting data for more than 10 years ago, some of our used telescopes were updated with new CCDs, producing that the pipeline was no longer functional. Currently, the pipeline works with data from the following telescopes: 
\begin{itemize}
\item La Silla Observatory: Danish 1.54 m (previous and after 2017) and REM.
\item Cerro Tololo Inter-American Observatory: SMARTS 0.9 m and 1 m.
\item Las Campanas Observatory: Warsaw, Swope, Du Pont.
\item Cerro Pachón: SOAR
\end{itemize}
